Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-09-23 bbbq_article.tex
Reviewed supmat, progress #69

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_1_fast/fig_f_tmh_mhc1_normalized.png}
  \caption{
    Normalized proportion of MHC-I epitopes overlapping with TMHs
    for a human, viral and bacterial proteome.
  }
  \label{fig:f_tmh_mhc1_normalized}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_1_fast/fig_f_tmh_mhc2_normalized.png}
  \caption{
    Normalized proportion of MHC-II epitopes overlapping with TMHs
    for a human, viral and bacterial proteome.
  }
  \label{fig:f_tmh_mhc2_normalized}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Relation between haplotype and TMH over-representation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Per MHC haplotype, we simulated random peptides and measured the
predicted IC50 using \verb;epitope-prediction; (for MHC-I) 
and netmhc2pan (for MHC-II). 
Here, we show the IC50 value per haplotype that
is used to determine if a peptide binds to the haplotype's MHC.

@@

>>>>

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_1_fast/fig_f_tmh_mhc1_normalized.png}
  \caption{
    Normalized proportion of MHC-I epitopes overlapping with TMHs
    for human, viral and bacterial proteomes.
    Legend: covid = SARS-CoV-2, flua = influenza A, hepa = hepatitis A,
    human = homo sapiens, myco = Mycobacterium tuberculosis, 
    polio = poliovirus, rhino = rhinovirus
  }
  \label{fig:f_tmh_mhc1_normalized}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_1_fast/fig_f_tmh_mhc2_normalized.png}
  \caption{
    Normalized proportion of MHC-II epitopes overlapping with TMHs
    for human, viral and bacterial proteomes.
    Legend: covid = SARS-CoV-2, flua = influenza A, hepa = hepatitis A,
    human = homo sapiens, myco = Mycobacterium tuberculosis, 
    polio = poliovirus, rhino = rhinovirus
  }
  \label{fig:f_tmh_mhc2_normalized}
\end{figure}

@@

@@

Per MHC haplotype, we simulated random peptides and measured the
predicted IC50 using \verb;epitope-prediction; (for MHC-I) 
and netmhc2pan (for MHC-II). 
Here, we show the IC50 value per haplotype that
is used to determine if a peptide binds to the haplotype's MHC.
Included in this figure is the MHCnuggets prediction tool,
by \cite{shao2020high}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Relation between haplotype frequency and TMH over-representation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

There is no relation between haplotype frequency and TMH over-representation.
